R for Clinical Study Reports and Submission

### 2021-09-02 tlf-baseline.Rmd
pass spell checking

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize critical demographic and baseline characteristics of the patients
in the section 11.2, demographic and other baseline characteristics of a CSR.

@@

There is many R packages that can effciently summarize baseline information.
The [`table1`](https://github.com/benjaminrich/table1) R package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and `RACE` in this example
using the `table1` R package. 
More details of the `table` R package can be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html)

@@

We start to define the format of the output. We highlighted items that 
is not discussed in previous discussion.

@@

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize critical demographic and baseline characteristics of the patients
in Section 11.2, Demographic and Other Baseline Characteristics.

@@

There is many R packages that can efficiently summarize baseline information.
The [`table1`](https://github.com/benjaminrich/table1) R package is one of them.

@@

For simplicity, we only analyze `SEX`, `AGE` and `RACE` in this example
using the `table1` R package. 
More details of the `table` R package can be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

@@

We start to define the format of the output. We highlight items that 
are not discussed in previous discussion.

@@

In conclusion, the procedure to generate demographic and baseline characteristics table is summarized as follows.

- Step 1: Read the data set.
- Step 2: Use `table1::table1()` to get the baseline characteristics table.
- Step 3: Transfer the output in Step 2 into a data frame that only contains ASCII character.
- Step 4: Define the format of the rtf table by using R package `r2rtf`.

### 2021-09-02 tlf-efficacy.Rmd

```{r}
gluc <- adlb %>%
  left_join(adsl %>% select(USUBJID, EFFFL), by = "USUBJID") %>%
  filter(EFFFL == "Y" & PARAMCD == "GLUC") %>% # PARAMCD is parameter code and here we focus on Glucose (mg/dL) 
  arrange(TRTPN) %>% 
  mutate(TRTP = factor(TRTP, levels = unique(TRTP)))

@@

```{r}
ana %>%
  select(USUBJID, TRTPN, AVISIT, AVAL, BASE, CHG) %>%  # AVAL: analysis value
                                                       # BASE: baseline value
                                                       # CHG: change from baseline
  head(4)
```
## Helper Functions

>>>>

```{r}
gluc <- adlb %>%
  left_join(adsl %>% select(USUBJID, EFFFL), by = "USUBJID") %>%
  # PARAMCD is parameter code and here we focus on Glucose (mg/dL) 
  filter(EFFFL == "Y" & PARAMCD == "GLUC") %>% 
  arrange(TRTPN) %>% 
  mutate(TRTP = factor(TRTP, levels = unique(TRTP)))

@@

- AVAL: analysis value
- BASE: baseline value
- CHG: change from baseline

```{r}
ana %>%
  select(USUBJID, TRTPN, AVISIT, AVAL, BASE, CHG) %>%  
  head(4)
```
## Helper Functions
